A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-03 pilot-publication/manuscript.Rmd
Continue adding results to text

# Results
Between `r start.date` and `r end.date`, we enrolled `r n.patients`
trauma patients from `r n.centres` participating centres. The ATLS arm
enrolled `r n.atls` patients, the PTC arm `r n.ptc` patients, and the
standard care arm `r n.control` patients. We trained a total of 
`r n.residents` residents, `r n.atls.residents` in ATLS, and 
`r n.ptc.residents` in PTC.

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table
\@ref(tab:sample-characteristics). Overall, the number of females were
`r n.females` (`r p.females`%), the median age was `r median.age`
years (IQR `r iqr.age`), and the median ISS and NISS were `r median.iss`
(IQR `r iqr.iss`) and `median.niss` (IQR `iqr.niss`) respectively. The 
number of admitted patients was `r n.admitted` (`r p.admitted`%). A 
total of `r n.m30d` (`r p.m30d`%) patients had the primary outcome of 
mortality at 30 days after arrival to the emergency department.

```{r sample-characteristics, echo = FALSE, results = "asis"}
table1::t1kable(sample.characteristics.table)
```

## Patient Participant Outcomes
A total of `r n.m30d.atls` ( `r p.m30d.atls`%) patients in the ATLS
arm had the primary outcome, compared to `r n.m30d.ptc` (
`r p.m30d.ptc`%) patients in the PTC arm, and `r n.m30d.control` (
`r p.m30d.control`%) patients in the standard care arm. The absolute risk
difference between the ATLS and PTC arm was `r arr.atls.ptc`% units
<!--(95% CI X - X)-->, between the ATLS and standard care arms 
`r arr.atls.control`% units <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r arr.ptc.control`% units <!--(95% CI X
-X)-->. The relative risk between the ATLS and PTC arm was 
`r rr.atls.ptc` <!--(95% CI X - X)-->, between the ATLS and standard care
arms `r rr.atls.control` <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r rr.ptc.control` <!--(95% CI X - X)-->.

>>>>

# Results
```{r}
females <- inline_text(overall.sample.characteristics.table,
  variable = patinfo__pt_gender,
  level = "Female"
)
median.age <- inline_text(overall.sample.characteristics.table,
  variable = patinfo__pt_age
)
median.iss <- inline_text(overall.sample.characteristics.table,
  variable = riss
)
median.niss <- inline_text(overall.sample.characteristics.table,
  variable = niss
)
m30d <- inline_text(overall.sample.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes"
)
```

Between `r start.date` and `r end.date`, we enrolled `r n.patients`
trauma patients from `r n.centres` participating centres. The ATLS arm
enrolled `r n.atls` patients, the PTC arm `r n.ptc` patients, and the
standard care arm `r n.control` patients. We trained a total of 
`r n.residents` residents, `r n.atls.residents` in ATLS, and 
`r n.ptc.residents` in PTC.

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table
\@ref(tab:sample-characteristics). Overall, the number of females were
`r females`, the median (IQR) age was `r median.age`
years, and the median ISS (IQR) and NISS (IQR) were `r median.iss` and `r median.niss` respectively. A total of `r m30d` patients had the primary outcome of mortality at 30 days after arrival to the emergency department.

```{r sample-characteristics, echo = FALSE, results = "asis"}
sample.characteristics.table
```

## Patient Participant Outcomes

```{r, echo = FALSE}
post.training.outcomes.table <- outcome.results.tables$ci.level.0.95[["Outcomes in all patients after training, by treatment arm"]]
m30d.atls <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "ATLS"
)
```

After training, a total of `r m30d.atls` patients in the ATLS
arm had the primary outcome, compared to `r n.m30d.ptc` (
`r p.m30d.ptc`%) patients in the PTC arm, and `r n.m30d.control` (
`r p.m30d.control`%) patients in the standard care arm. The absolute risk
difference between the ATLS and PTC arm was `r arr.atls.ptc`% units
<!--(95% CI X - X)-->, between the ATLS and standard care arms 
`r arr.atls.control`% units <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r arr.ptc.control`% units <!--(95% CI X
-X)-->. The relative risk between the ATLS and PTC arm was 
`r rr.atls.ptc` <!--(95% CI X - X)-->, between the ATLS and standard care
arms `r rr.atls.control` <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r rr.ptc.control` <!--(95% CI X - X)-->.
